---
title: "BZN Perf Infor"
author: "Philip Wikman"
date: "2025-05-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Conceptual Definition of EVPI
EVPI is the maximum amount a decision-maker should be willing to pay to eliminate all uncertainty in the model parameters. It represents the difference between the expected value of decision-making with perfect information and the expected value under current uncertainty.

## To calculate EVPI, you need:

A probability distribution (e.g. from PSA) for each uncertain parameter.

A net monetary benefit (NMB) framework:

NMB =(𝜆×Effectiveness)−Cost

where λ is the willingness-to-pay (WTP) threshold per QALY.

## Assuming you already have a PSA dataset (e.g., from 10,000 simulations), the steps are:

Step 1. Compute NMB for each strategy per simulation
Step 2. Find the optimal strategy per simulation
Step 3. Average best NMB across simulations (i.e., expected value with perfect information)
Step 4. Compute expected NMB of current best strategy (i.e., expected value under uncertainty)
Step 5. EVPI = EVwPI - EVwCI


```{r}
# Paquetes necesarios
library(dplyr)
library(ggplot2)
library(MASS)
library(tidyr)
library(ggplot2)
source("calculate_qalys_costs.R")
source("Simulate.R")
source("Simulate_t.R")
source("QalyCost.R")
source("invbeta.R")
source("generate_rr_lognormal.R")
```


```{r}
# Definir parámetros del modelo
cycle_length <- 1        # Longitud de cada ciclo (en años)
discount_rate <- 0.03    # Tasa de descuento anual
BestVariab<-as.numeric(as.vector(readRDS("BestVariab_100000.RDS")))
grupos_sexo<-c("Hombre", "Mujer")
states <- c("Chronic_Asymptomatic", "Cardiac", "Digestive", "Death")
grupos_edad<-c("15-19", "20-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59", "60-64", "65-69")
# Estados de salud

P_card<-BestVariab[1]
CaMorR<-BestVariab[2]
DiMorR<-BestVariab[3] # Cucunubá et al. Parasites&Vectors 2016
P_card_t<-BestVariab[1]*0.49
P_dig<-BestVariab[4]
P_dig_t<-BestVariab[4]*0.88

P_mort_m<-c(0.00015, 0.00037, 0.00044, 0.00054, 0.00077, 0.00095, 0.00161, 0.00289, 0.00543, 0.00893, 0.01401)
P_mort_W<-c(0.00014, 0.00016, 0.00015, 0.00023, 0.00037, 0.00062, 0.00096, 0.00158, 0.00273, 0.00429, 0.00648)

qaly_weights <- c(
  Chronic_Asymptomatic = 0.9625,
  Cardiac = 0.7171,
  Digestive = 0.80,
  Death = 0
)

costs <- c(
  Chronic_Asymptomatic = 478,
  Cardiac = 11976.53,
  Digestive = 858.82,
  Death = 0
)

discount_rate <- 0.03  # 3% discount rate
repeats<-1000
ParameterDat<-data.frame(matrix(NA, nrow=repeats, ncol=6))
psa_df<-matrix(NA, nrow=repeats, ncol=4)
colnames(PSADAT)<-c("AQALYs", "ACosts", "ICER")
set.seed(123)

  P_card<-invbeta(mu=0.0076, low=0.013, high=0.03, n=repeats)
  CaMorR<-generate_rr_lognormal(1.1,3,1.57, n=repeats)
  DiMorR<-generate_rr_lognormal(0.9,1.5, 1, n=repeats)
  P_dig<-invbeta(mu=0.027, low=0.008, high=0.035, n=repeats)
  RR_T_car<-generate_rr_lognormal(0.19,1.25,0.49, n=repeats)
  RR_T_dig<-generate_rr_lognormal(0.55,1.42,0.88, n=repeats)
  
for (i in 1:repeats){ 
  ParameterDat[i,1]<-P_card[i]
  ParameterDat[i,2]<-CaMorR[i]
  ParameterDat[i,3]<-DiMorR[i]
  ParameterDat[i,4]<-P_dig[i]
  ParameterDat[i,5]<-RR_T_car[i]
  ParameterDat[i,6]<-RR_T_dig[i]
}

for (i in 1:repeats){
### Simulating non-treatment arm
population_over_time<-Simulate(P_card=P_card[i], CaMorR=CaMorR[i], DiMorR=DiMorR[i], P_dig=P_dig[i], horizon=20)

### Simulating the treatment arm

population_over_time_t<-Simulate_t(P_card=P_card[i], CaMorR=CaMorR[i], DiMorR=DiMorR[i], P_dig=P_dig[i], RR_T_car=RR_T_car[i], RR_T_dig=RR_T_dig[i], horizon=20)


# Calculate Qalys and costs 
Det_CEA_H<-QalyCost(population_over_time, population_over_time_t)
# Assume psa_df is a data.frame with QALYs and costs for 2 strategies over N sims
psa_df[i,]<-as.numeric(c(Det_CEA_H[2,1], Det_CEA_H[1,1], Det_CEA_H[2,2], Det_CEA_H[1,2]))


# Progresion counter
cat(sprintf("\rProgress: %d%% | Iteration %d of %d", round(i / repeats * 100), i, repeats))
    flush.console()
}
# Convert PSADAT to a data frame
colnames(psa_df)<-c("QALYs_treated","QALYs_control", "Cost_treated", "Cost_control" )
psa_df
```

```{r}
psa_df<-as.data.frame(psa_df)
WTP <- 33895  # example threshold

psa_df <- psa_df %>%
  mutate(
    NMB_treated = WTP * QALYs_treated - Cost_treated,
    NMB_control = WTP * QALYs_control - Cost_control,
    Best_NMB = pmax(NMB_treated, NMB_control)
  )

EVwPI <- mean(psa_df$Best_NMB)
EVwPI
EVwCI <- max(mean(psa_df$NMB_treated), mean(psa_df$NMB_control))
EVwCI
EVPI <- EVwPI - EVwCI
EVPI
```
```{r}
psa_df <- psa_df %>%
  mutate(
    inc_NMB = NMB_treated - NMB_control,
    cum_mean_NMB = cumsum(inc_NMB) / row_number()
  )
ggplot(psa_df, aes(x = 1:nrow(psa_df), y = cum_mean_NMB)) +
  geom_line(color = "blue") +
  labs(
    title = "Convergence of Incremental Net Monetary Benefit (NMB)",
    x = "Number of Simulations",
    y = "Cumulative Mean Incremental NMB (€)"
  ) +
  theme_minimal()+ 
  geom_hline(yintercept = mean(psa_df$inc_NMB), linetype = "dashed", color = "red")

```
